Well-quasi-orderings on word languages

### 2025-10-17 src/appendix.tex
Fix additional grammar issues and verify compilation
Co-authored-by: AliaumeL <24816735+AliaumeL@users.noreply.github.com>

    In particular, letting $S_{\max}$ be the set of all maximal elements
    of $S$,
    we conclude that 
    \begin{equation*}
        L \subseteq S \cup \bigcup_{w \in S_{\max}} (\upset[\prefleq]{w}) \cap L
        \quad .
    \end{equation*}
    Hence, that $L$ is finite union of \kl{chains}.
\end{proofof}

@@

\begin{proofof}{small-ordinal-invariants:thm}
    It is always true that the \kl{ordinal height} of a language over a finite
    alphabet is at most $\omegaOrd$. Let us now consider a
    \kl{well-quasi-ordered} language $L$ that is \kl{downwards closed} for the
    \kl{infix relation}. Applying 
    \cref{dw-closed-wqo-charac:thm}, we can write $L = \bigcup_{i = 1}^n L_i$ where
    each $L_i$ is the set of finite \kl{infixes} of a finite, infinite or
    bi-infinite \kl{ultimately uniformly recurrent} word $w_i$.
   We can then
    directly conclude that $\oWidth{L_i}$ less than $\omegaOrd$ (in the case of
    a finite word), less than $\omegaOrd \cdot 2$ (in the case of an infinite
    word thanks to \cref{small-ordinal-invariants:lem}), or less than $3 \cdot
    \omegaOrd$ (in the case of a bi-infinite word, thanks to
    \cref{from-bi-to-single:lem}). In any case,
    we have the bound $\oWidth{L_i} < \omegaOrd \cdot 3$.

>>>>

    In particular, letting $S_{\max}$ be the set of all maximal elements
    of $S$,
    we conclude that 
    \begin{equation*}
        L \subseteq S \cup \bigcup_{w \in S_{\max}} (\upset[\prefleq]{w}) \cap L
        \quad .
    \end{equation*}
    Hence, $L$ is a finite union of \kl{chains}.
\end{proofof}

@@

\begin{proofof}{small-ordinal-invariants:thm}
    It is always true that the \kl{ordinal height} of a language over a finite
    alphabet is at most $\omegaOrd$. Let us now consider a
    \kl{well-quasi-ordered} language $L$ that is \kl{downwards closed} for the
    \kl{infix relation}. Applying 
    \cref{dw-closed-wqo-charac:thm}, we can write $L = \bigcup_{i = 1}^n L_i$ where
    each $L_i$ is the set of finite \kl{infixes} of a finite, infinite or
    bi-infinite \kl{ultimately uniformly recurrent} word $w_i$.
   We can then
    directly conclude that $\oWidth{L_i}$ is less than $\omegaOrd$ (in the case of
    a finite word), less than $\omegaOrd \cdot 2$ (in the case of an infinite
    word thanks to \cref{small-ordinal-invariants:lem}), or less than $3 \cdot
    \omegaOrd$ (in the case of a bi-infinite word, thanks to
    \cref{from-bi-to-single:lem}). In any case,
    we have the bound $\oWidth{L_i} < \omegaOrd \cdot 3$.
